% -*- TeX-engine: luatex; -*-

%     ___                             ___                  __   _______    __
%    /   |  ____  ___  ___  ____ _   /   |____  ____ _____/ /  / ____/ |  / /
%   / /| | / __ \/ _ \/ _ \/ __ `/  / /| /_  / / __ `/ __  /  / /    | | / /
%  / ___ |/ / / /  __/  __/ /_/ /  / ___ |/ /_/ /_/ / /_/ /  / /___  | |/ /
% /_/  |_/_/ /_/\___/\___/\__, /  /_/  |_/___/\__,_/\__,_/   \____/  |___/
%                           /_/


\documentclass[a4paper,11pt]{article}
\usepackage{romannum}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{array}
\usepackage[left=1.2in,top=1in,right=1.2in,bottom=1.1in]{geometry}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}

% \input{glyphtounicode}

\usepackage[T1]{fontenc}
\usepackage{inconsolata}

\usepackage{fontspec}
% \newfontfamily{\FAS}{fa6-Sharp-Regular-400.otf}
% \newfontfamily{\FAS}[Scale = 1]{fa6Pro-Regular-400.otf}
\newfontfamily{\FAS}[Scale = 1]{fa6Pro-Regular-400.otf}
\setmonofont{Iosevka}[SizeFeatures={Size=11}]

% \usepackage{helvet}
% \renewcommand\familydefault{\sfdefault}
% \usepackage{fontspec}
% \setmainfont{Cambria}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable


% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Muhammad Aneeq Asif} \\ \vspace{3pt}
    Bahawalpur, Pakistan 63210 \\ \vspace{2pt}
    \href{mailto:aneeqasifazada3@gmail.com}{\raisebox{-0.1\height}\faEnvelope\  \underline{aneeqasifazada3@gmail.com}} ~
    \href{https://www.linkedin.com/in/aneeqazad}{\raisebox{-0.1\height}\faLinkedin\ \underline{linkedin.com/in/aneeqazad}}  ~
    \href{https://github.com/Aneeqasif}{\raisebox{-0.1\height}\faGithub\ \underline{github.com/Aneeqasif}}
    \vspace{5pt}
\end{center}


%-----------EDUCATION-----------
%% \section{\faLightbulb[regular] Education}
\section[Education]{{\FAS  }  Education} %
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pakistan Institute of Engineering and Applied Sciences (PIEAS)}{Sep 2019 -- July 2023}
      {Bachelor of Science in Physics}{Nilore, Islamabad, Pakistan}
  \resumeSubHeadingListEnd

\vspace{-12pt}

  \resumeSubHeadingListStart
    \resumeSubheading
      {Punjab Group of Colleges (PGC)}{Sep 2017 -- July 2019}
      {Higher Secondary School Certificate with Mathematics}{Bahawalpur, Pakistan}
  \resumeSubHeadingListEnd
\vspace{-10pt}

%------RELEVANT COURSEWORK-------
\section[Relevant Coursework]{{\small \FAS{} }  Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-3pt, parsep=3pt, label=\faCaretRight]
                \item \small Solid State Physics \Romannum{1}, \Romannum{2}
                \item Electromagnetic Theory
                \item Physics of Semiconductor Devices
                \item Thermal and Statistical Physics
                \item Computer Simulations in Physics
                \item Quantum Mechanics
                \item Introduction to Quantum Optics
                \item Modern Physics
                \item Applied Chemistry
                \item Mathematical Methods of Physics
                \item Optics
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

\vspace{1pt}
%-----------EXPERIENCE-----------
\section[Experience]{{\FAS  } Experience}
% \section[Experience]{{\small \faIcon[regular]{arrow-alt-circle-up}} Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {National Centre for Physics}{July 2022 - Sep 2022}
      {Intern}{Islamabad, Pakistan}
      \resumeItemListStart
        \resumeItem{Designed and developed ANN model in \textbf{\texttt{\small PyTorch}} to predict the lattice energy of the crystal based on elemental properties and structural features.}
        \resumeItem{Hands on experience on using  \textbf{ \texttt{PROPhet} } machine learning C++ library.}
        \resumeItem{Thorough study of various fundamental machine learning models, including Decision Trees, PCA, Linear, Polynomial, Ridge, Logistic, and Lasso Regression, as well as splines, curve fitting, and Cross Validation techniques.}
        \resumeItem{Cleaning and pre-processing of Data generated by VASP in Python.}
      \resumeItemListEnd


    \resumeSubheading
      {PIEAS CISD HPC Department}{May 2019 -- August 2019}
      {Volunteer}{Islamabad, Pakistan}
      \resumeItemListStart
      \resumeItem{Offered Linux expertise to deploy the EasyBuild framework and install 15 different computational software packages, including VASP, Quantum ESPRESSO, OpenFOAM and many machine learning libraries in HPC cluster \textbf{Dunamis} at my university. I Configured installations to work with different compiler toolchains, ensuring compatibility and optimization for diverse computational needs.}
      \resumeItem{Setup and deployed Apptainer and Docker engine and installed the GPU-compliant Quantum Espresso Docker container from NVIDIA NGC Docker registry.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace{-16pt}

%-----------PROJECTS-----------
\section[Projects]{{\FAS  }Projects}
    % \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Machine Learning Assisted Discovery}  \hspace{2pt}   $|$ \emph{Final Year Research Project} \hspace{1.85in} \small \textbf{Sep 2022 - May 2023} \\ \small \textbf{of Superconductivity Equations
} }{}
          \vspace{-5pt}
          \resumeItemListStart
          \resumeItem{Successfully employed the Sure Independence Screening and Sparsifying Operator
                    (SISSO) framework to enhance the Allen-Dynes Equations for modeling the critical
                    temperature (Tc) of superconductivity.}
           \resumeItem{This involves Symbolic regression of Material predictors that extracted form spectral functions, generated
                    from Quantum Espresso EPW Package.}
           \resumeItem{We successfully introduce a correction factor to Allen-Dynes
                    equation of superconductivity that make the new formula more accurate and
                    realistic in modeling the phenomenon.}
          \resumeItemListEnd
          \vspace{-15pt}

      \resumeProjectHeading
          {\textbf{3 node Open-Mpi mini Cluster} $|$ \emph{Linux, Bash, OpenMpi}}{March 2023}
          \resumeItemListStart
          \resumeItem{Single-handedly built a three-node HPC cluster using OpenMPI, a leading message passing interface (MPI) implementation for
            parallel computing.}
            \resumeItem{Configured Quantum Espresso and ensured seamless communication among nodes.}
            \resumeItem{Implemented secure SSH access to the cluster nodes, ensuring remote accessibility for administration and job execution.}
            \resumeItem{Created user-friendly documentation for cluster usage and Provided hands-on training to Junior fellows.}
          \resumeItemListEnd
          \vspace{-15pt}

          \resumeProjectHeading
          {\textbf{Ising model Mote-Carlo Simulation} $|$ \emph{Python, Numpy, Matplotlib}}{December 2022}
          \resumeItemListStart
            \resumeItem{Completed term project on Monte Carlo study to
                        explore the behavior of the two-dimensional Ising model, a fundamental system in
                        statistical mechanics.}
            \resumeItem{Analyzed the system's phase transitions and critical phenomena.}
          \resumeItemListEnd
          \vspace{-15pt}


          \resumeProjectHeading
          {\textbf{Spherical Voronoi Diagrams} $|$ \emph{Python, Numpy, Matplotlib}}{December 2022}
          \resumeItemListStart
            \resumeItem{Developed Python program employing Spherical Voronoi Diagrams to map Earth's surface.}
            \resumeItem{Determined vertex coordinates in geographic coordinate
                        system and accurately measured areas of individual Voronoi polygons,
                        facilitating spatial analysis and geographic information systems (GIS)
                        applications.}
          \resumeItemListEnd
          \vspace{-15pt}

          \resumeProjectHeading
          {\textbf{Divorce Prediction Deep Neural Network} $|$ \emph{Python, Tensorflow, Keras, Matplotlib}}{Sep 2022}
          \resumeItemListStart
            \resumeItem{Developed an Artificial Neural Network using Python's Keras Sequential API to predict divorce probabilities between couples based on questionnaire data, achieving up to 95\% accuracy.}
          \resumeItemListEnd
          \vspace{-15pt}

          \resumeProjectHeading
          {\textbf{Simulation of Boltzmann Distribution} $|$ \emph{Python, Matplotlib}}{Nov 2022}
          \resumeItemListStart
            \resumeItem{Utilized Python to simulate Boltzmann Distribution, effectively modeling the velocity distribution of gas molecules and recovering the characteristic Boltzmann distribution of molecular speeds.}
          \resumeItemListEnd
          \vspace{-15pt}


          \resumeProjectHeading
          {\textbf{Custom Linux Configuration} $|$ \emph{Bash, Linux, Python, Lua, Elisp}}{Active}
          \resumeItemListStart
            \resumeItem{Designed and implemented a comprehensive Linux Desktop environment in python using Qtile library for efficient multitasking in daily workflow.}
            \resumeItem{Implemented scripts to deploy and configure system services, automating daily tasks such as automated Git backups, log monitoring, and push notifications for job completions to my Android.}
            \resumeItem{Maintain a functional Neovim configuration written in
                        Lua spanning 2,000 lines of code,and an 3K LOC Emacs configuration written in Elisp.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------PROGRAMMING SKILLS-----------
\section{{\FAS  } Technical Skills}
 % \begin{itemize}[leftmargin=0.15in, label={}]
 %    \small{\item{
 %     \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, SQL} \\
 %     \textbf{Developer Tools}{: VS Code, Eclipse, Google Cloud Platform, Android Studio} \\
 %     \textbf{Technologies/Frameworks}{: Linux, Jenkins, GitHub, JUnit, WordPress} \\
 %    }}
 % \end{itemize}

\begingroup
\small
\renewcommand{\arraystretch}{1.1}
\setlength{\tabcolsep}{8pt} % Adjust as needed
\begin{tabular}{ l l }
    \textbf{Programming Languages}: & Python, Lua, Julia, C, Bash, Mathematica \\
    \textbf{Libraries}: & Numpy, Pytorch, Matplotlib, Pandas, Qtile, scipy\\
    \textbf{Operating Systems}: & Debian based Distros, Arch Linux, Fedora, Centos\\
    \textbf{Tooling}: & GNU Plot, VS Code, Git, Github, Emacs, Neovim \\
\end{tabular}
\endgroup
\vspace{2mm}


\vspace{-12pt}

\section{{\FAS  }Online Courses}

% % \renewcommand{\arraystretch}{1.1}
% \setlength{\tabcolsep}{8pt} % Adjust as needed
% \begin{tabular}{ p{40mm} p{40mm} }
%   \textbf{Simulation and modeling of natural processes} \newline \emph{University of Geneva}
%   & \textbf{Discrete Optimization} \newline  \emph{The University of Melbourne} \\
% \end{tabular}

% \setlength{\columnsep}{-100pt}

% \begin{multicols}{2}
%     \begin{itemize}[itemsep=-3pt, parsep=3pt, label=\faCaretRight]
%         \item \textbf{Simulation and modeling of} \\
%         \textbf{natural processes} \\
%         \emph{University of Geneva}

%         \item \textbf{Discrete Optimization} \\
%         \emph{The University of Melbourne} \\

%         \item \textbf{The Finite Element Method} \\ \textbf{ for Problems in Physics} \\
%         \emph{University of Michigan}
%     \end{itemize}
% \end{multicols}


\begingroup
\small

\begin{multicols}{2}
    \begin{itemize}[itemsep=0pt, parsep=3pt, label=\faCaretRight]

      \item \parbox[t]{\linewidth}{\textbf{Discrete Optimization} \\
            \emph{The University of Melbourne}}

      \item \parbox[t]{\linewidth}{\textbf{Simulation and modeling} \\
            \textbf{of natural processes} \\
            \emph{University of Geneva}}

      \item \parbox[t]{\linewidth}{\textbf{The Finite Element Method} \\
            \textbf{ for Problems in Physics} \\
            \emph{The University of Melbourne}}

      \item \parbox[t]{\linewidth}{\textbf{Julia for Beginners in Data Science} \\
            \emph{Coursera Project Network }}

      \item \parbox[t]{\linewidth}{\textbf{Crash course in Gnuplot} \\
            \emph{Coursera Project Network }}

      \item \parbox[t]{\linewidth}{\textbf{Computational Thinking for} \\
            \textbf{Problem Solving} \\
            \emph{University of Pennsylvania}}

    \end{itemize}
\end{multicols}


\vspace{-1mm}

 \endgroup


\section{{\faPaperPlane[regular] }  Workshops}


    \resumeSubHeadingListStart
        \resumeSubheading{Introduction to Docker}{March 2024}{\textbf{Guest Speaker}}{PIEAS}
          \vspace{-5pt}
        \resumeSubheading{Data Science with Python}{Jan 2022}{Attendee}{PIEAS}
          \vspace{-5pt}
        \resumeSubheading{Deep Learning and its Application}{Dec 2022}{Attendee}{PIEAS}
          \vspace{-5pt}
        \resumeSubheading{Linux for Everyone}{Oct 2022}{\textbf{Guest Speaker}}{PIEAS}

    \resumeSubHeadingListEnd

% \vspace{-12pt}
%-----------INVOLVEMENT---------------
\section{{\FAS } Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{PIEAS Society for Physics}{Nov 2021 -- Jan 2023}{President}{PIEAS}
            \resumeItemListStart
              \resumeItem{Co-founded the Physics Society at PIEAS, leading a team to establish a platform for academic and social engagement among physics students.}
              \resumeItem{Organized multiple talks by renowned speakers and researchers, enriching members' understanding of cutting-edge research and developments.}
              \resumeItem{Led meetings, events, and activities to foster community and collaboration within the physics department.}
              \resumeItem{Developed strategic initiatives for academic and professional development, including guest lectures and workshops.}
              \resumeItem{Represented the society in meetings with university stakeholders, advocating for physics students' interests.}
            \resumeItemListEnd


        \resumeSubheading{Step Ahead Welfare Society}{Nov 2020 -- April 2021}{Volunteer}{Rawalpindi}
            \resumeItemListStart
              \resumeItem{Taught at a street school camp in Liaquat Bagh, providing essential education to underprivileged children from neighboring slum areas. Implemented educational programs focusing on foundational literacy and numeracy skills.}
              \resumeItem{Coordinated and executed community outreach initiatives to boost awareness and involvement, leading to a notable increase in attendance and active participation among the target demographic.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd



\end{document}
